Nested Sampling with Multiple Objective Functions

### 2018-06-20 doc/ms.tex
algorithm

\usepackage{dsfont}

@@

>>>>

\usepackage{algorithm2e}
\usepackage{dsfont}
\usepackage{setspace}

@@

\begin{algorithm}[!ht]
    \setstretch{1.35}
    Set $N$, the number of particles \\
    Set $M$, the number of reps \\
    Set $d$, the target depth in nats \\
    Compute $J = Nd$, the number of NS iterations per rep \\
    \For{i in 1:$M$}{
      Set initial threshold $(\ell_1^*, \ell_2^*) = (0, 0)$ \\
      Generate initial particles $(\xx_1, ..., \xx_N)$ from prior $\pi$ \\
      Generate a `direction' (probability distribution over objective functions) $\boldsymbol{p}$ \\
      \For{j in 1:$J$}{
          Choose an objective function $k$ according to $\boldsymbol{p}$ \\
          Find $c = \textnormal{argmin}(\lambda C \to L_k(\xx_C))$, the index of the worst particle \\
          Write out $\xx_c$ to disk as $\xx_{ij}$ with prior weight $w_{ij}$ proportional to $(1 - 1/N)^j$ \\
          Replace threshold element $\ell_c^*$ with $L_k(\xx_C)$ \\
          Replace particle $c$ with new particle generated from
            $\pi\times\mathds{1}(L_1 > \ell_1^*, L_2 > \ell_2^*)$          
      }
    }

    Set $(T_1, T_2)$, the temperatures of a canonical distribution of interest \\
    Compute $\hat{Z}(T_1, T_2) \leftarrow \sum_{ij} w_{ij}\left(L_1(\xx_{ij})/T_1 + L_2(\xx_{ij})/T_2\right) / \sum_{ij} w_{ij}$\\
  \vspace*{0.5em}
  \caption{The `Switch Sampling' algorithm.}
\end{algorithm}
